Return of the Linguist:\\Toward scalable parallel corpus generation for machine translation

### 2016-06-01 doc/paper.tex
added some references

As early as Jelinek's (in)famous quote from the 1980's that ``{\em Every time I fire a linguist, my performance goes up},'' both linguists and linguistics have been increasingly marginalized in natural language processing. 
More recently, for example, \mynewcite{collobert 2011 footnote 8} mention the possibility of ``{\em [ideally]...to learn from letter sequences rather than words},'' illustrating an AI-motivated desire to move away from even the most fundamental of linguistic concepts.
A specific instance of this overall trend is the gradual shift of machine translation (MT) away from classical linguistic rule-based approaches \mycitep{hutchins} to contemporary machine learning approaches, which underlie statistical phrase-based systems like Moses \mycitep{moses} and more recent neural network systems \mycitep{sutskever, bengio}.  
But in the end, even the most cutting-edge machine learning MT system relies crucially on multilingual parallel corpora, typically taken from external sources like multilingual parliamentary proceedings. 
This results in what we perceive to be a disproportionate amount of effort being dedicated to the machine learning component of machine translation, with the ever-important input corpora being treated almost as an afterthought.\footnote{
    Of course, these parallel corpora represent hundreds of translator-hours of work. 
    However, these translations are generally optimized for human consumption, not machine learning, with no regard for such niceties as sentence alignment.
    This is illustrated briefly in Section \ref{case_study}.
    }

@@

% TODO: table with change; also list best and worst 
% caption should mention that the difference between 
    % ALTHOUGH you would expect that it would improve all models, it's not clear whether 
Removing TED talk number 767 (over 200 lines), as well as 15 hand-picked lines with bad TER scores,

First, note that the scores improve, which is consistent with the observation that

@@

This results in a significant TER score change that is almost as large as the score difference between the highest and lowest ranking system from the evaluation campaign.  
BLEU scores \mycitep{bleu}, on the other hand, did not change much.

@@

% TODO: table and reference
\begin{table}[]
\centering
\label{table:tst2010}
\begin{tabular}{|l|l|l|}
\hline
 & BLEU & TER  \\ \hline
Full {\small \tt tst2010} & 11.2 & 77.0  \\ \hline
Purged {\small \tt tst2010} & 11.8 & 71.3  \\ \hline
%\hline
%{\small \tt tst2014} &  &   \\ \hline
% &  &   \\ \hline
\end{tabular}
\caption{By comparison, the difference between the baseline TER score and (not shown) } % TODO: caption
\end{table}

>>>>

As early as Jelinek's (in)famous quote from the 1980's that ``{\em Every time I fire a linguist, my performance goes up},'' both linguists and linguistics have been increasingly marginalized in natural language processing. 
More recently, for example, \mynewcite{collobert:2011} mention the possibility of ``{\em [ideally]...to learn from letter sequences rather than words},'' illustrating an AI-motivated desire to move away from even the most fundamental of linguistic concepts.
A specific instance of this overall trend is the gradual shift of machine translation (MT) away from classical linguistic rule-based approaches \mycitep{hutchins:2005} to contemporary machine learning approaches, which underlie statistical phrase-based systems like Moses \mycitep{moses} and more recent neural network systems \mycitep{sutskever:2014,bengio:2014}.  
But in the end, even the most cutting-edge machine learning MT system relies crucially on multilingual parallel corpora, typically taken from external sources like multilingual parliamentary proceedings. 
This results in what we perceive to be a disproportionate amount of effort being dedicated to the machine learning component of machine translation, with the ever-important input corpora being treated almost as an afterthought.\footnote{
    Of course, these parallel corpora represent hundreds of translator-hours of work. 
    However, these translations are generally optimized for human consumption, not machine learning, with no regard for such niceties as sentence alignment.
    This is illustrated briefly in Section \ref{case_study}.
    }

@@

% TODO: table with change; also list best and worst 
% caption should mention that the difference between 
    % ALTHOUGH you would expect that it would improve all models, it's not clear whether 
%Removing TED talk number 767 (over 200 lines), as well as 15 hand-picked lines with bad TER scores,

%First, note that the scores improve, which is consistent with the observation that 
% something to keep in mind in case reviewers ask

@@

@@

%This results in a significant TER score change that is almost as large as the score difference between the highest and lowest ranking system from the evaluation campaign.  
%BLEU scores \mycitep{bleu}, on the other hand, did not change much.

% no, omit this, because DUH, if you change the test set, the scores will change. (it's like changing your ruler.)
% TODO: table and reference
%\begin{table}[]
%\centering
%\label{table:tst2010}
%\begin{tabular}{|l|l|l|}
%\hline
% & BLEU & TER  \\ \hline
%Full {\small \tt tst2010} & 11.2 & 77.0  \\ \hline
%Purged {\small \tt tst2010} & 11.8 & 71.3  \\ \hline
%%\hline
%%{\small \tt tst2014} &  &   \\ \hline
%% &  &   \\ \hline
%\end{tabular}
%\caption{By comparison, the difference between the baseline TER score and (not shown) } % TODO: caption
%\end{table}
